---
title: "goal_organization"
author: "Bernice Cheung"
date: "3/9/2020"
output: html_document
---
### set the enviornment
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(svDialogs)
```

### load data & the log

Before downloading data from Qualtrics, data from people who didn't consent are filtered out. All data is downloaded directly to the folder ../FYP_rawdata
```{r}
# extract file information from the raw data folder
data_files <- file.info(Sys.glob("../FYP_rawdata/*.csv"))

# identify the latest created file
latest_file <- row.names(data_files)[which.max(data_files[["ctime"]])]

# load the data
df <- read.csv(latest_file)

# load the log
log <- read.csv("../FYP_rawdata/randomized_goals/randGoalLog.csv")

```

### set parameters for the randomization
```{r}
# Who is doing this randomization? 
researcher <- "BC"

# Who are the RAs? 
raNames <- c("JM", "VH", "AA", "AJ", "EO", "KW")

# How many RAs are required to rate a given item? 
teamSize <- 2
```


### organize goals
```{r}
# select relevant columns
goalDf <- df %>%
  select(grep("goal_list", names(df)))

# add the id column
goalDf$id <- df$id

# get rid of the first 2 rows that are not goals
goalDf <- goalDf[-c(1,2),]

```


### check the log
```{r}
# check the ID number of the last recorded case
lastId <- tail(log$lastSubjectNumber,1)

# check the row number of the last recorded case
lastRow <- which(goalDf$id == lastId)

# extract the total number of subject and goals
totalSubject <- tail(log$totalSubject,1)
totalGoals <- tail(log$totalGoals,1)
```

### randomize new goals
```{r}
# subset new goals
newDf <- goalDf[(lastRow+1):nrow(goalDf),] %>%
  select(-id)

# vectorize goals
newGoal <- as.vector(as.matrix(newDf))

# get rid off emply goal
newGoal <- newGoal[newGoal!=""]

# randomize goals
randGoal <- as.vector(sample(newGoal))
```

### generate RA pairs
```{r}
# randomize the order of the RA names
raNames <- sample(raNames)

# extract the total number of RAs
raNum <- length(raNames)
  
# generate all pairs of combination
raPairs <- combn(raNames, teamSize)

# transpose the matrix
raPairs <- t(raPairs)

# extract the number of pairs
pairNum <- nrow(raPairs)

# randomize the order of the ra pairs
raPairs <- raPairs[sample(pairNum),]
```

### assign goals to each pair
```{r}
# modify the length of the goals so that it can be devided by the number of pairs. The additional items will be NAs. 
length(randGoal) <- prod(dim(matrix(randGoal, nrow = pairNum)))

# assign goals across all pairs and transform the result into a dataframe 
goalMatrix <- matrix(randGoal, nrow = pairNum)
goalMatrix <- as.data.frame(goalMatrix)

# combine the output with the ra pairs
assignDf <- cbind(raPairs, goalMatrix)
```

### extract goals for each RA
```{r}
# calculate the maximum number of items assigned for each RA
rowMax <- length(randGoal) * (teamSize/raNum)

# initialize an empty dataframe where each RA is represented by a column
raDf <- data.frame(matrix(nrow = rowMax, ncol = raNum))
colnames(raDf) <- raNames

# loop through each RA and extract the goals assigned to the RA pairs that this RA belongs 
for (raIdx in 1:length(raNames)){
  ra <- raNames[raIdx]
  pairIdx <- which(raPairs == ra, arr.ind = T)[,1] # see which pair includes this RA
  goals <- goalMatrix[pairIdx,] # extract the goals from these pairs
  raGoals <- as.vector(as.matrix(goals)) # vectorize the goals 
  raDf[,raIdx] <- sample(raGoals) # randomize the order
}
```

### update the log
```{r}
newLog <- data.frame(researcher = researcher,
                     date = as.character(Sys.Date()),
                     lastSubjectNumber = tail(goalDf$id, 1),
                     nSubject = nrow(newDf),
                     nGoals = length(newGoal),
                     totalSubject = totalSubject + nrow(newDf),
                     totalGoals = totalGoals + length(newGoal))

updatedLog <- rbind(log, newLog)
```


### write the files
```{r}
# write the randomized output
write.csv(raDf, paste0("../FYP_rawdata/randomized_goals/randomizeGoal_",Sys.Date(),".csv"), row.names = F)

# write the updated log
write.csv(updatedLog, "../FYP_rawdata/randomized_goals/randGoalLog.csv", row.names = F)
```

